Dynamic Modeling, Parameter Estimation and Uncertainty Analysis in \proglang{R}

### 2016-10-19 article.tex
Availability

@@

@@

A system of ordinary differential equation $\dot x = f(x, p, u, t)$ is represented by a named \code{character} vector of symbolic expressions, the right-hand side of the ODE, involving symbols for the states $x$, the parameters $p$, the forcings $u$ and the keyword \code{time} for $t$. The names of the vector are the state names. The class provided by \pkg{dMod} for such objects is the \code{eqnvec} class which checks whether the character can be parsed and thus, can be interpreted as an equation.

>>>>

The \pkg{dMod} package is available on the Comprehensive \proglang{R} Archive Network at \url{http://CRAN.R-project.org/package=dMod}. The project is hosted on GitHub, \url{https://github.com/dkaschek/dMod}, where the most recent development version is available.

@@

\vspace{4em}

@@

A system of ODEs $\dot x = f(x, p, u, t)$ is represented by a named \code{character} vector of symbolic expressions, the right-hand side of the ODE, involving symbols for the states $x$, the parameters $p$, the forcings $u$ and the keyword \code{time} for $t$. The names of the vector are the state names. The class provided by \pkg{dMod} for such objects is the \code{eqnvec} class which checks whether the character can be parsed and thus, can be interpreted as an equation.
